### 2018-11-20 articleSFDS.tex
début correction relecture anglais

\startlocaldefs
% Commandes auteurs spécifiques, par exemple :
\newcommand{\EP}[1]{\textcolor{blue}{(eric): #1}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mbox{\tiny \`eme}}
\def\1{1\kern-.20em {\rm l}}
\endlocaldefs

@@

\begin{aug}
    \auteur{
      \prenom{Mathieu} 
      \nom{Carmassi}
      \thanksref{t1,t2,t3}
      \contact[label=e1]{mathieu.carmassi@edf.fr}
      \contact[label=e1Bis]{mathieu.carmassi@agroparistech.fr}
      	}
    \and
    \auteur{
      \prenom{Pierre} 
      \nom{Barbillon}
      \thanksref{t2}
      \contact[label=e2]{pierre.barbillon@agroparistech.fr}
    	}
    \and
    \auteur{
      \prenom{Merlin} 
      \nom{Keller}
      \thanksref{t3}
      \contact[label=e4]{merlin.keller@edf.fr}
	    }
	\and
    \auteur{
      \prenom{Eric} 
      \nom{Parent}
      \thanksref{t2}
      \contact[label=e5]{eric.parent@agroparistech.fr}
  		}
    \and
    \auteur{
      \prenom{Matthieu} 
      \nom{Chiodetti}
      \thanksref{t1}
      \contact[label=e3]{matthieu.chiodetti@edf.fr}
    	}

@@

\begin{abstract}
Les difficultés de mise en oeuvre d'expériences de terrain ou de laboratoire, ainsi que les coûts associés, conduisent les sociétés 
industrielles à se tourner vers des codes numériques de calcul. Ces codes, censés être représentatifs des phénomènes physiques en jeu, 
entraînent néanmoins tout un cortège de problèmes. Le premier de ces problèmes provient de la volonté de prédire la réalité à partir d'un 
modèle informatique. En effet, le code doit être représentatif du phénomène et, par conséquent, être capable de simuler des données proches de  
la réalité. Or, malgré le constant développement du réalisme de ces codes, des erreurs de prédiction subsistent. Elles sont de deux natures différentes. La
première provient de la différence entre le phénomène physique et les valeurs relevées expérimentalement. La deuxième concerne l'écart entre le code développé et le phénomène physique. Pour diminuer cet écart, souvent qualifié de biais ou d'erreur de modèle, les développeurs complexifient en général les codes, les rendant très chronophages dans certains cas. De plus, le code dépend de paramètres à fixer par l'utilisateur qui doivent être choisis pour correspondre au mieux aux données de terrain. L'estimation de ces paramètres propres au code s'appelle le calage.
Ce papier propose une revue des méthodes de calage bayésien et s'appuie sur un cas d'application qui permet de discuter les divers choix méthodologiques et d'illustrer leurs divergences. Cet exemple s'appuie sur un code de calcul servant à prédire la puissance d'une centrale photovoltaïque.

@@

\begin{altabstract}
Field experiments are often difficult and expensive to make. To bypass these issues, industrial companies have developed computational codes. These codes intend to be representative of the physical system, but come with a certain amount of problems. The code intends to be as close as possible to the physical system. It turns out that, despite continuous code development, the difference between the code outputs and experiments can remain significant. Two kinds of uncertainties are observed. The first one comes from the difference between the physical phenomenon and the values recorded experimentally. The second concerns the gap between the code and the physical system. To reduce this difference, often named model bias, discrepancy, or model error, computer codes are generally complexified in order to make them more realistic. These improvements lead to time consuming codes. Moreover, a code often depends on parameters to be set by the user to make the code as close as possible to field data. This estimation task is called calibration. This paper proposes a review of Bayesian calibration methods and is based on an application case which makes it possible to discuss the various methodological choices and to illustrate their divergences. This example is based on a code used to predict the power of a photovoltaic plant.

@@

Numerical experiments have become increasingly popular in many (if not all) industrial fields. Indeed, setting up field experiments can represent a huge investment for a company. Numerical simulations are generally considered as a substitute to bypass physical or field experiments \citep{santner2013,fang2005}. However, the complexity of computer codes, used in such simulations, increases with the capacity of computer processors, and sometimes at a much higher rate. The consequence is straightforward\hc some codes have become greedy in computational time \citep{sacks1989}. Moreover, a gap between computer code outputs and field measures of the physical process, sought to simulate, is routinely observed. 
Checking the accuracy of the code by confronting it with field experiments is called validation \citep{bayarri2007}. This task is difficult since it is based on a few unavoidable field data and a computational code, often long to run. 
All along this paper, we will use the word ``code'' as a proxy for numerical code, sometimes also called numerical model, simulator or computational code and field experiment for real world experiment.
\newline

@@

A code output is then written as $f_c(\boldsymbol{x},\boldsymbol{\theta})$ whereas $\zeta(\boldsymbol{x})$ denotes the output of the physical phenomenon for the same variable $\boldsymbol{x}$. This is of course an idealized formalization, in which we assume that the code variables $\boldsymbol{x}$ are exhaustive to describe the phenomenon of interest, in the sense that the quantity to be predicted can take a single deterministic value $\zeta(\boldsymbol{x})$ for a given $\boldsymbol{x}$. 
In this paper, the quantity of interest is assumed to be a scalar but 
extensions with high dimension outputs are
possible \citep{higdon2008}. 
Therefore, in what follows, the images of $\zeta$ and $f_c$ lie in $\mathbb{R}$.
\newline

@@

Calibrating the code consists
in making the vector of parameters $\boldsymbol{\theta}$ consistent in some sense with these $n$ field data. In an industrial framework, uncertainty quantifications \citep{rocquigny2009quantifying} can be decomposed into a step by step procedure and calibration is identified as a key element of the so-called \textit{step B'}. As illustrated in \citet{damblin2015}, this step concerns calibration,
verification and validation (V\&V). V\&V can be further split into 3 phases  described in \citet{roache1998}, \citet{bayarri2007} and \citet{oberkampf1998}.
Calibration then aims at finding the "best" parameter vector $\boldsymbol{\theta}=\boldsymbol{\theta}^*$ such that the error term made by the
code in a statistical model is minimal. Several statistical modeling strategies have been proposed in the literature. When only measurement errors
are considered, \citet{cox2001} use a rather simple model, considering that the code does not differ from the phenomenon under study. As for
\citet{higdon2004}, \citet{kennedy2001} and \citet{bayarri2007},  they advocate some extensions, which additionally encompass a \textit{model bias} 
or a \textit{model error} term, also dubbed \textit{discrepancy} in the following. All of these models are reviewed and discussed in Section
\ref{sec:calibration}. The identifiability issues between the parameter $\boldsymbol{\theta}$ and the discrepancy were already discussed in the written discussions of \citet{kennedy2001}. \citet{tuo2015efficient} consider the calibration task as a minimization of a loss function between the code and the physical reality. 
In \citet{tuo2016theoretical}, 
%they interpret the definition of \citet{kennedy2001} for $\boldsymbol{\theta}$ (the ``best-fitting'' parameter) as being the minimizer of the reproducing kernel Hilbert space norm based on the prior distribution of the discrepancy.
they show that this loss function leads to an estimation of $\boldsymbol{\theta}$ depending on the chosen prior distribution of the discrepancy. Then,  \citet{plumlee2017} advices an orthogonality 
specification for the discrepancy i.e. the discrepancy should be orthogonal to the gradient of the computer code with respect to a loss function.
\newline

As an industrial illustrative example, we will focus, in this paper, on predicting the energy production from a photovoltaic (PV) plant \citep{martin2001}. The industrial context is to go through proposals as a manufacturer and a supplier for PV plants. The selling price announced by the industrial company has to be competitive enough to be successful in the bidding process. Of course, the building costs and the production over the plant lifetime have to be known to evaluate the profit margins. Although a best guess-estimate, the deterministic evaluation of PV production through a sophisticated computer code, does not fulfill the needs of a financial investor in  PV projects. To evaluate the financial risks of his/her investment and consequently to make his decision, the investor needs to assess the uncertainty around the expected production estimation. To do so, all the sources of uncertainties have to be identified and treated in their current form. Calibration will be useful for hunting down the uncertainties related to the modeling and quantify the range of the main potential errors made in predicting the profit ratio.\newline

%\paragraph{Plan de l'article}

@@

The code, hereafter considered as a ``black box'', is a solver of the main equations mimicking the electrical behavior of the PV plant. All along the article the code will represent a PV test stand with 12 panels connected together. The considered power will be the one before the inverter (multiplication of the continuous current and continuous voltage). Fortunately, for an in-depth exploration of the complete range of situations encountered in the domain of Bayesian calibration of computer codes, the ``black box'' code $f_c$ appears to be fast for the case study (one launch needs only $39\mu s$ to run). To investigate what happens when the code is time consuming, we will simply slow it down by restructuring the number of runs allowed for the computer code $f_c$.
%, as an artificial dirty but fruitful trick played to the computer code.
The code depends on some parameter vector $\boldsymbol{\theta}$ and input variables $\boldsymbol{x}$ detailed as follows (also called general inputs in \citet{plumlee2017}): $\boldsymbol{\theta}=\begin{pmatrix}
\eta \\
\mu_t \\
n_t \\
a_l \\
a_r\\
n_{inc}
\end{pmatrix}$ and $\boldsymbol{x}=\begin{pmatrix}
t\\
L\\
l\\
I_g\\
I_d \\
T_e
\end{pmatrix}$. \newline

The physical meaning of parameters is explained below \citep{duffie2013}\hc 
\begin{itemize}
\item $\eta$\hc module photo-conversion efficiency,
\item $\mu_t$\hc module temperature coefficient (the efficiency decreases when the temperature rises) in \%/°$C$,
\item $n_t$\hc reference temperature for the normal operating conditions of the module in °$C$,
\item $a_l$\hc reflection power of the ground (albedo),
\item $a_r$\hc describe the transmission of the radiation as a function of the incidence angle of solar rays, which depends on optical properties and the cleanliness,
%\item $h_{cw}$, $h_{c}$: convection coefficients
\item $n_{inc}$\hc transmission factor for normal incidence. \newline
\end{itemize}

@@

Note that some temporal aspect is taken into account through the input variables. We do not consider any delay in the PV reaction to the forcing conditions. Time $t$ indicates here a snap shot corresponding to the instant when the power has to be computed. This code only focuses on a specific time and if the evolution of the power over a day is what we look for, a repetition over the specific durations has to be made. This operation has to consider the number of time steps available. For example, if $300$ configurations of $\boldsymbol{x}$ are accessible for one day, the code will have to be executed $300$ times to have the power evolution over a day. For the rest of the article, we will denote the code output referring to the i\textsuperscript{th} time step by $f_c(\boldsymbol{x}_i,\boldsymbol{\theta})$ and by $f_c(\textbf{X},\boldsymbol{\theta})$ the code outputs corresponding to the whole time frame contained in matrix $\textbf{X}$. \newline

A sensitivity analysis performed according to the screening method of Morris \citep{morris1991} has showed that only the variations of $\eta$, $\mu_t$ and $a_r$ have a significant impact on the power. This sensitivity analysis consists in evaluating with elementary displacements in a normalized input space, the responses to these displacements on the output. To testify that $\eta$, $\mu_t$ and $a_r$ have a significant impact over a whole duration but not instantaneously a PCA (Principal Component Analysis) is performed on all outputs generated for the duration and for all combinations of the design of experiments (DOE) of Morris. On the new uncorrelated basis of the space, the information is summed up by a new Morris plot. This representation allows to visualize all the information summarized over the duration on one plot. However, to  implement such a method, the input space parameter needs to be well defined. That is why the work of the experts is really important. They have to define the range of each parameter as best as they can.\newline

@@

So far, experts are using the code with some parameter values with the knowledge that these parameters are uncertain (the so called reference values). They can also provide more expertise on the nature of the parameter. For example for $a_r$, the nominal value is $0.17$ and experts state that the parameter lies within the $95\%$ confidence interval $[0.05,0.29]$. We chose to consider $a_r$ as Gaussian with $a_r\sim\mathcal{N}(\mu=0.17,\sigma^2=3.6.10^{-3})$. The standard deviation is chosen equal to $0.06$ because we have considered the upper bound and the lower bound of the given interval as respectively the quantiles $a_{r_{0.975}}$ and $a_{r_{0.025}}$. Similarly, $\eta$ and $\mu_t$ are taken as Gaussian such as $\eta\sim\mathcal{N}(\mu=0.143,\sigma^2=2.5.10^{-3})$ and $\mu_t\sim\mathcal{N}(\mu=-0.4,\sigma^2=10^{-2})$. If $100$ realizations are drawn from the joint distribution of $\eta$, $\mu_t$ and $a_r$, the production curve and the \textit{prior} credibility interval can be simultaneously plotted on a same graph to see how uncertain the predicted power is over a day. Figure \ref{fig:ParamError} illustrates on the left the distribution of $\eta$, $\mu_t$ and $a_r$ and on the right the production curve obtained for reference values and the \prior credibility interval at $90\%$. On the right side, experiments collected that same day are also displayed. One can check that the prior credibility interval, built thanks to the experts, looks coherent regarding the experimental data.\newline

@@

  \caption{$\pi(\eta)$, $\pi(\mu_t)$ and $\pi(a_r)$ prior densities (represented on the left panel) and induced credibility interval of the instantaneous power (right panel)}
  \label{fig:ParamError}
\end{figure}

If one is interested in the energy produced rather than the power (the energy in $kWh$ is the power in $kW$ multiplied by a duration), one can easily compute the maximum and the minimum energy for say $100$ realizations. The energy for collected power is $W_{exp}=3.44 kWh$, the maximum energy computed $W_{max}=3.65 kWh$ and the minimum energy $W_{min}=2.93 kWh$. Straightforwardly $W_{min} < W_{exp} < W_{max}$ which means that the experts interval seems correct for that day. With the considered uncertainty on $\eta$, $\mu_t$ and $a_r$, the error made is about $20\%$ over only one day. 
Considering this error over a day, cumulative error over a lifetime plant could be too prejudicial. The aim of the calibration is to quantify this error and, at the same time, increase the knowledge on the parameter distribution.
%If we consider this error as constant, cumulative error over a lifetime plant could be too prejudicial. The aim of the calibration is to decrease this error on the output. 
The results of calibration for this application case are detailed in Section \ref{sec:application}.

@@

Calibration intends to find the ``best fitting'' parameters of a computational code, in order to minimize the difference between the output and the experiments. The variance of the measurement error is also unknown and has to be estimated as well as the parameters but will be considered as a nuisance parameter. It can be used in two cases. In a forecasting context \citep{craig2001}, where the calibrated code on data collected on site can be used to compute the behavior of the power plant over the next time period. But also, in a prediction context, where data from an experimental stand are used to predict the behavior of a non-existing stand (assuming they have the same features). \newline

@@

%The difficulties implied by such a model appear quickly. Indeed, to realize calibration, we need to compare for each candidate parameter value $\boldsymbol{\theta}$, the computer code output $f_c(\boldsymbol{x}_i,\boldsymbol{\theta})$ corresponding to each available observation $y_{exp_i}$.
%
%Actually, to estimate parameters, the maximum likelihood estimation could be a way to reach this purpose. To realize it, a lot of code calls are necessary. Especially in a Bayesian framework, where the update of a \prior  distribution with a likelihood is looked for, the number of runs are really important (straightforwardly linked to the number of runs in a Markov Chain Monte Carlo (MCMC) \cite{robert1996}). When the code is time-consuming, these methods become unrealistic.

The likelihood of such a model is a function of $f_c$. In methods such as Maximum Likelihood Estimation (MLE) or as in Bayesian estimation (making recourse to many MCMC iterations), it becomes intractable to work with a time consuming $f_c$.\newline

For the sake of simplicity we will consider, in what follows, the code as deterministic. It means that for the same inputs, the output of the code is identical, which is generally the case. Even in a deterministic context, a gap between the code and the physical system is often unavoidable. This gap is called code error or discrepancy. Some papers advocate for adding this discrepancy in the statistical models \citep{kennedy2001,higdon2004,bayarri2007,bachoc2014}. In the following, we present three models which take into account a time consuming code and/or an additional discrepancy.
\newline

% Three different models are presented in the paper from this point which are conditioned by the issues mentioned above.
%
%Moreover, what is the legitimacy of the code regarding the physical system? Actually, a discrepancy often appears between the code and the physical system and has to be taken into account. Finally, a repetition of a code with same inputs could be different (stochastic code). For the sake of simplicity we will consider, for the rest of the article, the code as deterministic. We will therefore deal with the two remaining issues discussed above, which are: the code's computational complexity, and the presence of a discrepancy. These have motivated the development of several models which are described below. In this section, an overview of these models is given first. Then, the different likelihoods relative to each models will be detailed. Third, multiple ways to estimate the hyperparameters will be presented.

%In the first section, an overview of these models is given. The second section will deal with the establishment of the likelihood depending on the different model. The third section will highlight the multiple ways to estimate parameters. This will lead to the part where the models are tested in the frame of our application case and where choices are presented and explained.

@@

%An analytic form as a stochastic process would allow to compute this surrogate as many times as we want. A limited number of run of the time consuming code gives us simulated data and can help to design this surrogate. In \cite{sacks1989}, the stochastic process chosen is a Gaussian process defined by its mean and covariance functions (see the appendix \ref{ap:GaussianProcesses} for more details).

\begin{eqnarray}
\mathcal{M}_2 \ : \ \forall i \in \llbracket1,\dots,n\rrbracket \quad y_{exp_i} &=& F(\boldsymbol{x}_i,\boldsymbol{\theta}) + \epsilon_i,
\label{eq:M2}\\
F(\bullet,\bullet) & \sim &{\mathcal{GP}}{\Big(m_S(\bullet,\bullet),c_S\{(\bullet,\bullet),(\bullet,\bullet)\}\Big)},
\nonumber
\end{eqnarray}
where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$ and the random function $F(\boldsymbol{x}_i,\boldsymbol{\theta})$ stands for a Gaussian process (GP) over the joint domain of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. For the following, we consider that the measurement error is independent from the error made by the Gaussian process. The mean function $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ is generally a linear form of simple functions of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. Its covariance function $c_S\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}=\sigma_S^2 r_{\boldsymbol{\psi}_S}\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}$ is such as the function $r_{\boldsymbol{\psi_S}}\{(\bullet,\bullet),(\bullet,\bullet)\}$ is the correlation function with a vector parameter $\boldsymbol{\psi}_S$. This parameter vector represents the scale and the regularity of the kernel and where $\sigma_S^2$ represents the variance. The mean $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ can be written as\newline

@@

%As the other model introduced by \citet{higdon2004} and \citet{bayarri2007} only deals with changes on the discrepancy, the partial likelihood remains identical as the one for the model in \citet{bayarri2007}. \newline

@@

% The equation can be applied to our case by:

>>>>

\startlocaldefs
% Commandes auteurs spécifiques, par exemple :
\newcommand{\EP}[1]{\textcolor{blue}{(eric): #1}}
\newcommand{\new}[1]{\textcolor{blue}{ #1}}

\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mbox{\tiny \`eme}}
\def\1{1\kern-.20em {\rm l}}
\endlocaldefs

@@

\begin{aug}
    \auteur{
      \prenom{Mathieu} 
      \nom{Carmassi}
      \thanksref{t1,t2,t3}
      \contact[label=e1]{mathieu.carmassi@edf.fr}
      \contact[label=e1Bis]{mathieu.carmassi@agroparistech.fr}
      	}
    \and
    \auteur{
      \prenom{Pierre} 
      \nom{Barbillon}
      \thanksref{t2}
      \contact[label=e2]{pierre.barbillon@agroparistech.fr}
    	}
    \and
    \auteur{
      \prenom{Matthieu} 
      \nom{Chiodetti}
      \thanksref{t1}
      \contact[label=e3]{matthieu.chiodetti@edf.fr}
        }
	\and
    \auteur{\prenom{Merlin} 
      \nom{Keller}
      \thanksref{t3}
      \contact[label=e4]{merlin.keller@edf.fr}
	  	}
    \and
    \auteur{
      \prenom{Eric} 
      \nom{Parent}
      \thanksref{t2}
      \contact[label=e5]{eric.parent@agroparistech.fr}
  	}

@@

\begin{abstract}
Les difficultés de mise en \oe uvre d'expériences de terrain ou de laboratoire, ainsi que les coûts associés, conduisent les sociétés 
industrielles à se tourner vers des codes numériques de calcul. Ces codes, censés être représentatifs des phénomènes physiques en jeu, 
entraînent néanmoins tout un cortège de problèmes. Le premier de ces problèmes provient de la volonté de prédire la réalité à partir d'un 
modèle informatique. En effet, le code doit être représentatif du phénomène et, par conséquent, être capable de simuler des données proches de  
la réalité. Or, malgré le constant développement du réalisme de ces codes, des erreurs de prédiction subsistent. Elles sont de deux natures différentes. La
première provient de la différence entre le phénomène physique et les valeurs relevées expérimentalement. La deuxième concerne l'écart entre le code développé et le phénomène physique. Pour diminuer cet écart, souvent qualifié de biais ou d'erreur de modèle, les développeurs complexifient en général les codes, les rendant très chronophages dans certains cas. De plus, le code dépend de paramètres à fixer par l'utilisateur qui doivent être choisis pour correspondre au mieux aux données de terrain. L'estimation de ces paramètres propres au code s'appelle le calage.
Ce papier propose une revue des méthodes de calage bayésien et s'appuie sur un cas d'application qui permet de discuter les divers choix méthodologiques et d'illustrer leurs divergences. Cet exemple s'appuie sur un code de calcul servant à prédire la puissance d'une centrale photovoltaïque.

@@

\begin{altabstract}
Field experiments are often difficult and expensive to carry out. To bypass these issues, industrial companies have developed computational codes. These codes are intended to be representative of the physical system, but come with a certain number of problems. Despite continuous code development, the difference between the code outputs and experiments can remain significant. Two kinds of uncertainties are observed. The first one comes from the difference between the physical phenomenon and the values recorded experimentally. The second concerns the gap between the code and the physical system. To reduce this difference, often named model bias, discrepancy, or model error, computer codes are generally complexified in order to make them more realistic. These improvements increase the computational cost of the code. Moreover, a code often depends on user-defined parameters in order to match field data as closely as possible. This estimation task is called calibration. This paper proposes a review of Bayesian calibration methods and is based on an application case which makes it possible to discuss the various methodological choices and to illustrate their divergences. This example is based on a code used to predict the power of a photovoltaic plant.

@@

Numerical experiments have become increasingly popular in many (if not all) industrial fields, as setting up field experiments can represent a huge investment for a company. Numerical simulations are generally considered as a substitute to bypass physical or field experiments \citep{santner2013,fang2005}. However, the complexity of the computer codes used in such simulations increases with the capacity of computer processors, and sometimes at a much higher rate. As a result, some codes have become greedy in computational time \citep{sacks1989}. Moreover, a gap between computer code outputs and field measures of the physical process that the code seeks to simulate is routinely observed. 
Checking the accuracy of the code by confronting it with field experiments is called validation \citep{bayarri2007}. This task is difficult since it is based on a few unavoidable field data and a computational code, often long to run. 
All along this paper, we will use the word ``code'' as a proxy for numerical code, sometimes also called numerical model, simulator or computational code and field experiment for real world experiment.
\newline

@@

A code output is then written as $f_c(\boldsymbol{x},\boldsymbol{\theta})$ whereas $\zeta(\boldsymbol{x})$ denotes the output of the physical phenomenon for the same variable $\boldsymbol{x}$. This is of course an idealized formalization, in which we assume that the code variables $\boldsymbol{x}$ are exhaustive to describe the phenomenon of interest, in the sense that the quantity to be predicted can take a single deterministic value $\zeta(\boldsymbol{x})$ for a given $\boldsymbol{x}$. 
In this paper, the quantity of interest is assumed to be a scalar but 
extensions with high dimension outputs are
possible \citep{higdon2008}. 
Therefore, in what follows, the outputs of $\zeta$ and $f_c$ lie in $\mathbb{R}$.
\newline

@@

Calibrating the code consists
in making the vector of parameters $\boldsymbol{\theta}$ consistent in some sense with these $n$ field data. In an industrial framework, uncertainty quantifications \citep{rocquigny2009quantifying} can be decomposed into a step by step procedure and calibration is identified as a key element of the so-called \textit{step B'}. As illustrated in \citet{damblin2015}, this step concerns calibration,
verification and validation (V\&V). V\&V can be further split into 3 phases  described in \citet{roache1998}, \citet{bayarri2007} and \citet{oberkampf1998}.
Calibration then aims at finding the "best" parameter vector $\boldsymbol{\theta}=\boldsymbol{\theta}^*$ such that the error term made by the
code in a statistical model is minimal. Several statistical modeling strategies have been proposed in the literature. When only measurement errors
are considered, \citet{cox2001} use a rather simple model, considering that the code does not differ from the phenomenon under study while
\citet{higdon2004}, \citet{kennedy2001} and \citet{bayarri2007} advocate for some extensions which encompass a \textit{model bias} 
or a \textit{model error} term, also dubbed as \textit{discrepancy} in the following. All of these models are reviewed and discussed in Section
\ref{sec:calibration}. The identifiability issues between the parameter $\boldsymbol{\theta}$ and the discrepancy were already discussed in the written discussions of \citet{kennedy2001}. \citet{tuo2015efficient} consider the calibration task as a minimization of a loss function between the code and the physical reality. 
In \citet{tuo2016theoretical}, they show that this loss function leads to an estimation of $\boldsymbol{\theta}$ depending on the chosen \textit{prior} distribution of the discrepancy. Then,  \citet{plumlee2017} advices an orthogonality 
specification for the discrepancy \textit{i.e.} the discrepancy should be orthogonal to the gradient of the computer code with respect to a loss function.
\newline

As an industrial illustrative example, we will focus, in this paper, on predicting the energy production from a photovoltaic (PV) plant \citep{martin2001}. The industrial context is to go through proposals as a manufacturer and a supplier for PV plants. The selling price announced by the industrial company has to be competitive enough to be successful in the bidding process. Of course, the building costs and the production over the plant lifetime have to be known to evaluate the profit margins. Although a best guess-estimate, the deterministic evaluation of PV production through a sophisticated computer code, does not fulfill the needs of a financial investor in  PV projects. To evaluate the financial risks of his/her investment and consequently to make his decision, the investor needs to assess the uncertainty around the expected production estimation. To do so, all the sources of uncertainties have to be identified and treated in their current form. Calibration will be useful for hunting down the uncertainties related to the modeling and quantify the range of the main potential errors made in predicting the profit ratio. \new{This real case study will allow us to emphasize the differences between the statistical models used for calibration in a context where the statistical hypotheses usually made are not guaranteed to be valid.}
\newline

%\paragraph{Plan de l'articile}

@@

The code, hereafter considered as a ``black box'', is a solver of the main equations mimicking the electrical behavior of the PV plant. All along the article the code will represent a PV test stand with 12 panels connected together. The considered power will be the one before the inverter (multiplication of the continuous current and continuous voltage). Fortunately, for an in-depth exploration of the complete range of situations encountered in the domain of Bayesian calibration of computer codes, the ``black box'' code $f_c$ appears to be fast for the case study (one launch needs only $39\mu s$ to run). To investigate what happens when the code is time consuming, we will simply slow it down by restructuring the number of runs allowed for the computer code $f_c$. The code depends on some parameter vector $\boldsymbol{\theta}$ and input variables $\boldsymbol{x}$ detailed as follows (also called general inputs in \citet{plumlee2017}): $\boldsymbol{\theta}=\begin{pmatrix}
\eta \\
\mu_t \\
n_t \\
a_l \\
a_r\\
n_{inc}
\end{pmatrix}$ and $\boldsymbol{x}=\begin{pmatrix}
t\\
L\\
l\\
I_g\\
I_d \\
T_e
\end{pmatrix}$. \newline

The physical meaning of parameters is explained below \citep{duffie2013}\hc 
\begin{itemize}
\item $\eta$\hc module photo-conversion efficiency,
\item $\mu_t$\hc module temperature coefficient (the efficiency decreases when the temperature rises) in \%/°$C$,
\item $n_t$\hc reference temperature for the normal operating conditions of the module in °$C$,
\item $a_l$\hc reflection power of the ground (albedo),
\item $a_r$\hc describe the transmission of the radiation as a function of the incidence angle of solar rays, which depends on optical properties and the cleanliness,
\item $n_{inc}$\hc transmission factor for normal incidence. \newline
\end{itemize}

@@

Note that some temporal aspect is taken into account through the input variables. We do not consider any delay in the PV reaction to the forcing conditions. Time $t$ indicates here a snap shot corresponding to the instant when the power has to be computed. This code only focuses on a specific time and if the evolution of the power over a day is what we look for, a repetition over the specific duration has to be made. This operation has to consider the number of time steps available. For example, if $300$ configurations of $\boldsymbol{x}$ are accessible for one day, the code will have to be executed $300$ times to have the power evolution over a day. For the rest of the article, we will denote the code output referring to the i\textsuperscript{th} time step by $f_c(\boldsymbol{x}_i,\boldsymbol{\theta})$ and by $f_c(\textbf{X},\boldsymbol{\theta})$ the code outputs corresponding to the whole time frame contained in matrix $\textbf{X}$. \newline

A sensitivity analysis performed according to the screening method of Morris \citep{morris1991} has showed that only the variations of $\eta$, $\mu_t$ and $a_r$ have a significant impact on the power. This sensitivity analysis consists in evaluating with elementary displacements in a normalized input space, the impacts of these displacements on the output. To demonstrate that $\eta$, $\mu_t$ and $a_r$ have a significant impact over a whole duration but not instantaneously a PCA (Principal Component Analysis) is performed on all outputs generated for the duration and for all combinations of the design of experiments (DOE) of Morris. On the new uncorrelated basis of the space, the information is summed up by a new Morris plot. This representation allows us to visualize all the information summarized over the duration on one plot. However, to  implement such a method, the input space parameter needs to be well defined. That is why the work of the experts is really important. They have to define the range of each parameter as best as they can.\newline

@@

So far, experts are using the code with some parameter values with the knowledge that these parameters are uncertain (the so called reference values). They can also provide more expertise on the nature of the parameter. For example for $a_r$, the nominal value is $0.17$ and experts state that the parameter lies within the $95\%$ confidence interval $[0.05,0.29]$. We chose to consider $a_r$ as Gaussian with $a_r\sim\mathcal{N}(\mu=0.17,\sigma^2=3.6.10^{-3})$. The standard deviation is chosen equal to $0.06$ because we have considered the upper bound and the lower bound of the given interval as respectively the quantiles $a_{r_{0.975}}$ and $a_{r_{0.025}}$. Similarly, $\eta$ and $\mu_t$ are taken as Gaussian such as $\eta\sim\mathcal{N}(\mu=0.143,\sigma^2=2.5.10^{-3})$ and $\mu_t\sim\mathcal{N}(\mu=-0.4,\sigma^2=10^{-2})$. If $100$ realizations are drawn from the joint distribution of $\eta$, $\mu_t$ and $a_r$, the production curve and the \textit{prior} credibility interval can be simultaneously plotted on a same graph to see how uncertain the predicted power is over a day. Figure \ref{fig:ParamError} illustrates on the left the distribution of $\eta$, $\mu_t$ and $a_r$ and on the right the production curve obtained for reference values and the \prior credibility interval at $90\%$. On the right side, experiments collected that same day are also displayed. One can check that the \textit{prior} credibility interval, built thanks to the experts, looks coherent regarding the experimental data.\newline

@@

  \caption{$\pi(\eta)$, $\pi(\mu_t)$ and $\pi(a_r)$ \textit{prior} densities (represented on the left panel) and induced credibility interval of the instantaneous power (right panel)}
  \label{fig:ParamError}
\end{figure}

If one is interested in the energy produced rather than the power (the energy in $kWh$ is the power in $kW$ multiplied by a duration), one can easily compute the maximum and the minimum energy for say $100$ realizations. The energy for collected power is $W_{exp}=3.44 kWh$, the maximum energy computed $W_{max}=3.65 kWh$ and the minimum energy $W_{min}=2.93 kWh$. Straightforwardly $W_{min} < W_{exp} < W_{max}$ which means that the experts interval seems correct for that day. With the considered uncertainty on $\eta$, $\mu_t$ and $a_r$, the error made is about $20\%$ over only one day. 
Considering this error over a day, cumulative error over a lifetime plant could be too prejudicial. The aim of the calibration is to quantify this error and, at the same time, increase the knowledge on the parameter distribution. The results of calibration for this application case are detailed in Section \ref{sec:application}.

@@

Calibration intends to find the ``best fitting'' parameters of a computational code, in order to minimize the difference between the output and the experiments. \new{The variance of the measurement error is also unknown and has to be estimated as well as the parameters but will be considered as a nuisance parameter. It can be used in two cases.} In a forecasting context \citep{craig2001}, where the calibrated code on data collected on site can be used to compute the behavior of the power plant over the next time period. But also, in a prediction context, where data from an experimental stand are used to predict the behavior of a non-existing stand (assuming they have the same features). \newline

@@

The likelihood of such a model depends on $f_c$. In methods such as Maximum Likelihood Estimation (MLE) or as in Bayesian estimation (making recourse to many MCMC iterations), it becomes intractable to work with a time consuming $f_c$.\newline

For the sake of simplicity we will consider, in what follows, the code as deterministic. It means that for the same inputs, the output of the code is identical, which is generally the case. Even in a deterministic context, a gap between the code and the physical system is often unavoidable. This gap is called code error or discrepancy. Some papers advocate for adding this discrepancy in the statistical models \citep{kennedy2001,higdon2004,bayarri2007,bachoc2014}. In the following, we present three other models which take into account a time consuming code and/or an additional discrepancy.
\newline

@@

\begin{eqnarray}
\mathcal{M}_2 \ : \ \forall i \in \llbracket1,\dots,n\rrbracket \quad y_{exp_i} &=& F(\boldsymbol{x}_i,\boldsymbol{\theta}) + \epsilon_i,
\label{eq:M2}\\
F(\bullet,\bullet) & \sim &{\mathcal{GP}}{\Big(m_S(\bullet,\bullet),c_S\{(\bullet,\bullet),(\bullet,\bullet)\}\Big)},
\nonumber
\end{eqnarray}
where $\forall i \in \llbracket1,\dots,n\rrbracket \quad \epsilon_i\overset{iid}{\sim}\mathcal{N}(0,\sigma_{err}^2)$ and the random function $F(\boldsymbol{x}_i,\boldsymbol{\theta})$ stands for a Gaussian process (GP) over the joint domain of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. \new{For the following, we consider that the measurement error is independent on the error made by the Gaussian process}. The mean function $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ is generally a linear form of simple functions of $\boldsymbol{x}_i$ and $\boldsymbol{\theta}$. Its covariance function $c_S\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}=\sigma_S^2 r_{\boldsymbol{\psi}_S}\{(\boldsymbol{x}_i^*,\boldsymbol{\theta}^*),(\boldsymbol{x}_i,\boldsymbol{\theta})\}$ is such as the function $r_{\boldsymbol{\psi_S}}\{(\bullet,\bullet),(\bullet,\bullet)\}$ is the correlation function with a vector parameter $\boldsymbol{\psi}_S$. This parameter vector represents the scale and the regularity of the kernel and where $\sigma_S^2$ represents the variance. The mean $m_{S}(\boldsymbol{x}_i,\boldsymbol{\theta})$ can be written as\newline

@@

@@
